Drawing Trees and Animating Tree Changes

### 2010-05-14 paper/paper.tex
Small changes, needs merging
Lots of reflowing of text, but nothing major.

Paper from 1996 and Tamassia and FruchetermanWhatever magnets and springs
model.

@@

Our library is written in Java, and users of the library need only use two of the classes it contains: the \java{Tree} class, and the \java{TreeDisplay} class.

\subsection{How-To}
\subsection{A Sample Application}

@@

>>>>

Paper from 1996 and Tamassia and the force-directed placement algorithm\cite{fdp}.

@@

Our library is written in Java, and users of the library need only use two of
the classes it contains: the \java{Tree} class, and the \java{TreeDisplay}
class.  Our primary design principle in building this system was ease of usage
by another programmer.  Therefore, our two classes have very few methods, and
those few methods are very simple to use.  Prior efforts focused a lot of work
on making specific animations efficient, but we have instead focused our
efforts on ease of use.

\subsection{How-To}

The class \java{TreeDisplay} needs to only be created once.  A
\java{TreeDisplay} is an AWT component, and may be used as such in any Java
code.  A \java{Tree} may be created at any time, and to display a tree, use the
\java{setTree} method of the \java{TreeDisplay} class.

\subsection{A Sample Application}

@@

\bibliographystyle{plain}
\bibliography{bibliography.bib}
